Proposed Solution

### 2016-01-29 system.tex
reduce type section

Configuration files usually consist of variable assignments, or some simple instructions about including files or libraries. We initially
collect all assignments into a set of pairs $(n, v)$, where $n$ denotes 
variable name and $v$ denotes variable value. However, based only on the 
value $v$ we cannot determine the type of $n$.

Consider for instance the following example:\\
\texttt{\hspace*{2em}foo = 300\\
\hspace*{2em}bar = 300.txt}\\
Most likely \texttt{foo} is an integer, but it could also be a string.
In the latter case we want to learn the rule $ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. We introduce {\emph{probabilistic types}} to 
address this issue.

Let $\mathcal{T}$ be a set of basic types. In \app set $\mathcal{T}$ contains strings, integers, file paths, sizes and IP addresses. 
A probabilistic type built from $\mathcal{T}$ is a list of pairs $[(\tau_1, p_1),\ldots,(\tau_n, p_n)]$ such that $\tau_i \in \mathcal{T}$, 
$0 \le p_i \le 1$ 
and $\Sigma p_i = 1$. These probabilities are learned from the training 
corpus.

When a value has a probabilistic type, we generate rules for all its types. This means that by assigning {\texttt{foo}} a probabilistic type 
(e.g. $(\texttt{foo}, 300, [(\textsl{Int},90\%),(\textsl{String},10\%)])$
we now generate rules for strings and integers.

For a given value, its probabilistic type is updated over time. When the type inference uniquely determines the type, the probability of all other types is set to zero, and  the associated rules are withdrawn.

This idea is closely related to existentially quantified types \cite{Launchbury93lazyfunctional}.

>>>>

Each line of a configuration files can be reduced to a keyword value pair
In the parsing step we collect all lines in the file into a set of such pairs $(k, v)$, where $k$ denotes 
variable name and $v$ denotes variable value. 
However, based only on a single example value of $v$ we cannot fully determine the type of $k$.
We instead assign a distribution of type to a value, an idea is closely related to existentially quantified types \cite{Launchbury93lazyfunctional}.

Consider for instance the following example:\\
\texttt{\hspace*{2em}foo = 300\\
\hspace*{2em}bar = 300.txt}\\
Most likely \texttt{foo} is an integer and we learn an equality rule, but it could also be a string.
In this case we want to learn the rule $ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. 
For more advanced rules, we may need to even compose these types to learn complex rules.
We introduce {\emph{probabilistic types}} to address this issue.

Let $\mathcal{T}$ be a set of basic types. In \app set $\mathcal{T}$ contains strings, integers, file paths, sizes and IP addresses. 
A probabilistic type built from $\mathcal{T}$ is a list of pairs $[(\tau_1, p_1),\ldots,(\tau_n, p_n)]$ such that $\tau_i \in \mathcal{T}$, 
$0 \le p_i \le 1$ 
and $\Sigma p_i = 1$. These probabilities are updated each time a new example value for a keyword is encountered.
When a value has a probabilistic type, we generate rules for all its types. This means that by assigning {\texttt{foo}} a probabilistic type 
(e.g. $(\texttt{foo}, 300, [(\textsl{Int},90\%),(\textsl{String},10\%)])$
we now generate rules for both strings and integers.
Once the type inference can uniquely determine the type, the probability of all other types is set to zero, and the associated rules are withdrawn.
